% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number
\name{\bf Sichen Li}

\section{\bf Contact Information}
\datedsubsection{School of Mathematics, East China University of Science and Technology}{}
\datedsubsection{Room 702, Teaching Building 8, Xuhui Campus, 130 Meilong Road,Shanghai, 200237,China}{}
\datedsubsection{Email: sichenli@ecust.edu.cn}{}
\datedsubsection{Homepage: https://sichenag.github.io/home/}{}
\section{\bf Education}
\datedsubsection{Sep. 2014 -- Jun. 2020}{Ph. D, School of Mathematical Sciences, East China Normal University}
\datedsubsection{Jul. 2018 -- Feb. 2020}{CSC student, Department of Mathematics, National University of Singapore}
\datedsubsection{Sep. 2010 -- Jun. 2014}{B.S., Faculty of Mathematics and Statistics, Hubei University}
\section{\bf Employment}
\datedsubsection{Aug. 2022-- Present}{School of Mathematics, East China University of Technology and Science}
\datedsubsection{May 2020-- Jun. 2022}{Postdoctoral Fellow, School of Mathematical Sciences, Fudan University}
\section{\bf Research}
\datedsubsection{Birational geometry of algebraic varieties and explicit birational geometry inspired by dynamics}{}
\subsection{\bf Accepted articles}
\begin{enumerate}
\item  Sichen Li and  Yohsuke Matuszawa, A note on Kawaguchi-Silverman conjecture, Internat. J. Math. \textbf{32} (2021), no. 11, 2150085.
\item Sichen Li, Bounding cohomology on a smoot projective surface with Picard number 2, Comm. Algebra. \textbf{49}(2021), no. 7, 3140-3144.
\item Hu Fei and Sichen Li, Free abelian groups actions on normal projective varieties: submaximal dynamical rank case, Canad. J. Math. \textbf{73}(2021), no. 4, 1053-1073. 
\item  Sichen Li, Derived length of zero entropy groups acting on projective varieties in arbitrary characteristic, A remark to a paper of Dinh-Oguiso-Zhang, Internat. J. Math. \textbf{31}(2020), no. 8, 2050059. 
\item Sichen Li, A note on a smooth projective surface with Picard number two, Math. Narch. \textbf{292}(2019), no. 12, 2637-2642. 
\end{enumerate}
\subsection{\bf Preprints}
\begin{enumerate}
\item Sichen Li, Zariski dense orbit conjecture on birational automorphisms of projective threefolds, submitted for publication, arXiv:2208.02616.
\item Sichen Li, Kawaguchi-Silverman conjecture on birational automorphisms of projective threefolds, submitted for publication,arXiv:2209.06815.
\item Sichen LI, Bounding cohomology on a smooth projective surface with Picard number two revisited, submitted for publication, arXiv:2103.01161.
\end{enumerate}
\section{\bf Travel (Since 2022)}
\begin{itemize}
\item 16 September 2022, visiting Chen Jiang, Shanghai Center for Mathematical Sciences, Fudan University, Shanghai,China
\item 23 June 2022- 31 August 2022,  visiting Jingjun Han and Chen Jiang, Shanghai Center for Mathematical Sciences, Fudan University, Shanghai,China
\item 18-25 February  2022, visiting Yaxiong Chen, Sanya Technology Innovation Park, Wuhan University of Technology, Sanya, China
\end{itemize}
\section{\bf Conferences (Since 2022)}
\begin{itemize}
\item  30 August 2022, Recent Development in Algebraic Geometry (online), Department of Mathematics, Faculty of Science, National University of Singapore
\item   18-22 July 2022, 3rd National Algebraic Geometry Conference (online), School of Mathematical Sciences and Shanghai Center for Mathematical Sciences, Fudan University
\item  11-12 June 2022,  China Southeastern Algebraic Geometry Symposium (II)(online), School of Mathematics, Sun Yat-sen University
\end{itemize}
\section{\bf Talks (Since 2019)}
\begin{itemize}
\item  4-6 November 2021, A survey on Kawaguchi-Silverman conjecture, Algebraic Geometry Forum, Soochow University, Suzhou, China
\item Jul. 7, 2021, Bounding cohomology on a smooth projective surface, Hubei University, Wuhan, China
\item   11 October 2019, Derived length of zero entropy groups acting on projective varieties in arbitrary characteristic -- A remark to a paper of Dinh-Oguiso-Zhang, Algebraic Geometry Seminar, East China Normal University, Shanghai,China 
\item  1-5 July  2019, A note on a smooth projective surface with Picard number 2, The 2nd National Algebraic Geometry Conference, PhD talk, East China Normal University, Shanghai, China 
\item  28 June 2019, A note on a smooth projective surface with Picard number 2, Hubei University, Wuhan, China 
\item   25 June 2019, Algebraic varieties with automorphism groups of sub-maximal dynamical rank, Algebraic Geometry Seminar, East China Normal University ,Shanghai, China 
\item  24 June 2019, Free abelian group actions on normal projective varieties,Tianyuan talk, Soochow University, Suzhou, China
\item  23 June 2019, Free abelian group actions on normal projective varieties,Shanghai Normal Unverisity, Shanghai, China 
\item  17 April 2019, A note on a smooth projective surface with Picard number 2, Topology and Geometry Seminar, National University of Sigapore, Singapore
\end{itemize}
\section{\bf Service}
\datedsubsection{September  2020 -- Present}{Mathematical Reviews Reviewer}
\datedsubsection{May 2018 -- Present}{Zentralblatt  Math  Reviewer}
\section{\bf Honors and Awards}
\datedline{December  2019}{National Scholarship for Doctoral Students, East China Normal University}
\datedline{September 2014}{Scholarship for Outstanding Postgraduate Students, East China Normal University}
\section{\bf References}
\datedsubsection{Prof. Meng Chen}{School of Mathematical Sciences, Fudan University}{Email: mchen@fudan.edu.cn}
\datedsubsection{Prof. Sheng-Li Tan}{School of Mathematical Sciences, East China Normal University}{Email: sltan@math.ecnu.edu.cn}
\datedsubsection{Prof. Rong Du}{School of Mathematical Sciences, East China Normal University}{Email: rdu@math.ecnu.edu.cn}


\end{document}
